The K2 Bright Star Survey

### 2019-05-31 paper/ms.tex
aerts edits

\subsection{Oscillating Red Giants}
\label{sec:rgs}
31 of the evolved stars in our sample have detectable stochastically-excited solar-like acoustic oscillations. In the asymptotic limit, these consist of a comb of modes separated by the large frequency separation \Dnu, approximately the sound-crossing-time of the star, with a Gaussian envelope centred on the frequency of maximum power \numax, which scales with the acoustic cutoff frequency at the star's surface. These can be used to constrain stellar fundamental parameters, and detailed studies of the deviations from this asymptotic limit for acoustic $p$-modes, for example due to their interaction with gravity-wave $g$-modes, can be used to accurately determine the stellar evolutionary state, for example to distinguish hydrogen shell burning red giant branch from helium core burning red clump stars. Summary plots for a good example of such a star, $\eta$~Cancri, are shown in Figure~\ref{fig:etacnc}.

>>>>

\subsection{Oscillating Red Giants}
\label{sec:rgs}
31 of the evolved stars in our sample have detectable stochastically-excited solar-like acoustic oscillations. In the asymptotic limit, these consist of a comb of modes separated by the large frequency separation \Dnu, approximately the sound-crossing-time of the star, with a Gaussian envelope centred on the frequency of maximum power \numax, which scales with the acoustic cutoff frequency at the star's surface. 
These \Dnu and \numax values can be used to constrain stellar fundamental parameters, such as radius, mass, and age \citep[e.g.][, for a recent review]{2017A&ARv..25....1H}. Detailed studies of the deviations from the asymptotic limit for p-modes, e.g. due to acoustic glitches, provide information on the He content and mixing processes at the bottom of the convective envelope \citep[e.g. ][]{Verma2019}. On the other hand, dipole mixed modes, which have a g-mode character in the inner regions of the star, fulfil an asymptotic period spacing determined by the buoyancy frequency inside the star. This spacing can be used to accurately determine the stellar evolutionary state and allow to distinguish between hydrogen shell and core helium burning \citep{bedding2011}. 
Summary plots for a good example of such a star, $\eta$~Cancri, are shown in Figure~\ref{fig:etacnc}.
